---
title: "irisPitch"
author: "Aman Jha"
date: "1/19/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Summary

- We here have created a model for prediction of Species of iris all the other features .

- This can be seen by plot below.
```{r}
pairs(iris)
```
```{r include=FALSE,echo=FALSE}
library(caret)
library(ggplot2)
```

## Model Fitting

We fit a **random forest** which provides a nearly perfect accuracy.This can be shown by dividing the dataset into traning and test set and fitting the appropriate model.
```{r echo=FALSE , cache=TRUE}
set.seed(344345)
inTrain<- createDataPartition(iris$Species,p=0.75,list=FALSE)
training<- iris[inTrain,]
testing<- iris[-inTrain,]

fit1<- train(Species~.,data=training,method="rf",
             trControl=trainControl(method="repeatedcv",number =10,repeats = 3))
pred<- predict(fit1,testing)
confusionMatrix(pred,testing$Species)
```

## App Documentation
- The app created requires the user to input the Sepal.Length,Sepal.Width,Petal.Length and Petal.Width such that it can predict the Species of the iris.
- After you add the values using slider input , you click on submit button to see the species your plant.
- The check box if clicked shows you the graph and your values in the particular graph. 
- You can enter values again and again for different obs.
- App is present at https://amanjha8.shinyapps.io/irisPrediction/


## Plot-1
```{r echo=FALSE}
ggplot(iris,aes(Petal.Length,Petal.Width,color=Species))+geom_point()
```

## Plot-2
```{r echo=FALSE}
ggplot(iris,aes(Sepal.Length,Sepal.Width,color=Species))+geom_point()
```

## THANKS!!